Probability Distribution Checks

### 2017-05-10 Probability_distribution_checks.Rmd
Update probability distribution checks

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS15$AUDPS, "norm")

@@

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS156 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS156$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS156$AUDPS, "norm")

>>>>

### Normal
```{r norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS15$AUDPS, "norm")
```

### Exponential

```{r exp, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$AUDPS, "exp")
```

@@

Until the issue with more diseased tillers than tillers in a hill is addressed,
this section will not work completely and properly.

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS156 <- subset(AUDPS, YEAR == "2016")
# f1 <- fitdist(AUDPS156$AUDPS, "norm")
#plot(f1)
car::qqp(AUDPS156$AUDPS, "norm")
